---
title: "Analysis of weights for the COVID Beliefs, Behaviors & Norms Survey"
output:
  html_document:
    df_print: paged
---

```{r}
library(readr)
library(ggplot2)
theme_set(theme_bw())
library(dplyr)
library(tidyr)
library(srvyr)
library(countrycode)
library(stringr)
```

## Load data
```{r}
# relies on setting environment variable COVID_SURVEY_DATA_DIR
both_surveys = read_tsv(
  paste0(Sys.getenv("COVID_SURVEY_DATA_DIR"), "covid_survey_responses.txt.gz"),
  col_types = cols(
    us_state = col_character(),
    india_state = col_character(),
    geoip_state = col_character(),
    wave = col_double(),#col_integer(),
    weight_demo = col_double(),
    weight_full_survey = col_double(),
    trim_indicator_demo = col_integer(),
    trim_indicator_full_survey = col_integer(),
    weight_internet_demo = col_double(),
    weight_internet_full_survey = col_double(),
    trim_indicator_internet_demo = col_integer(),
    trim_indicator_internet_full_survey = col_integer(),
    prevention_mask = col_character()
    )
  )
```

```{r}
both_surveys = both_surveys %>% 
  mutate(
    country_code = countrycode::countrycode(country, origin = "country.name", destination = "iso2c")
  )
waves = both_surveys %>% filter(survey_type == "waves", wave == 1)
```


# Trimming analysis
Are there multiple distinct values for weights that have been trimmed?
```{r}
both_surveys %>%
  filter(!is.na(weight_full_survey)) %>%
  group_by(country) %>%
  mutate(
    mean_weight_full_survey = mean(weight_full_survey)
  ) %>%
  filter(trim_indicator_full_survey == 1 & weight_full_survey > mean_weight_full_survey) %>%
  summarise(
    n_trimmed_weights_demo = n(),
    distinct_trimmed_weights_demo = n_distinct(weight_full_survey)
  ) %>%
  filter(distinct_trimmed_weights_demo > 1) %>%
  arrange(-distinct_trimmed_weights_demo)
```

Combine missingness categories, thus assuming any remaining missingness is MCAR. And create modified variables.
```{r}
waves_long = waves %>%
  filter(wave == 1, !is.na(country)) %>%
  mutate(across(everything(), na_if, -1)) %>%
  mutate(across(everything(), na_if, -2)) %>%
  mutate(
    female = gender == "Female",
    `age [18, 30]` = age %in% c("Under 20", "20-30"),
    `age > 50` = age %in% c("51-60", "61-70", "71-80", "Over 80"),
    know_positive_case = know_positive_case == "Yes",
    vaccine_accept = vaccine_accept == "Yes"
  ) %>%
  select(
    country, country_code,
    weight_demo, weight_full_survey, weight_internet_demo, weight_internet_full_survey,
    female, `age [18, 30]`, `age > 50`, know_positive_case, vaccine_accept) %>%
  pivot_longer(female:vaccine_accept)
  
```



# Using weights

## Using demographic completion weights
```{r}
w_v_uw_long = waves_long %>%
  filter(!is.na(weight_demo)) %>%
  as_survey_design(weights = weight_demo) %>%
  group_by(country, country_code, name) %>%
  summarise(
    n = unweighted(n()),
    unweighted = unweighted(mean(value, na.rm = TRUE)),
    weighted = survey_mean(value, na.rm = TRUE, vartype = "ci", deff = TRUE)
  ) %>%
  group_by(country) %>%
  mutate(
    female_unweighted = unweighted[name == "female"]
  )
```


## Demographic callibration with demographic completion weights
```{r}
w_v_uw_long %>% 
  filter(name %in% c("female", "age [18, 30]", "age > 50")) %>%
ggplot(
  aes(x = reorder(substr(country, 1, 27), female_unweighted),
      y = weighted, ymax = weighted_upp, ymin = weighted_low)
) +
  facet_wrap(~ name, scales = "free_x") +
  coord_flip() +
  geom_point(aes(y = unweighted), color = "brown", pch = 15) +
  geom_point() +
  geom_errorbar(width = .2) +
  scale_y_continuous(breaks = c(0, .25, .5)) +
  ylab("Weighted mean and 95% CI (black) and unweighted mean (brown)") +
  xlab("Country (sorted by unweighted % female)") +
  theme(panel.grid.minor = element_blank())
ggsave("../figs/calibration_demographics_by_country_demo_weights.pdf", width = 7, height = 4.5)
ggsave("../figs/calibration_demographics_by_country_demo_weights.png", width = 7, height = 4.5, dpi = 400)
```

## Design effects
```{r}
w_v_uw_long %>% 
  filter(name %in% c("know_positive_case", "vaccine_accept")) %>%
  mutate(
    name = gsub("accept", "acceptance", gsub("_", " ", name))
  ) %>%
ggplot(
  aes(x = reorder(substr(country, 1, 27), weighted_deff, max),
      y = weighted_deff, color = name, shape = name, group = name)
) +
  #facet_wrap(~ name, scales = "free_x") +
  coord_flip() +
  geom_point(size = 2) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_sqrt(breaks = seq(1, 5, by = .5), lim = c(1, 5)) +
  ylab("Design effect") +
  xlab("Country (sorted by max design effect)") +
  theme(panel.grid.minor = element_blank(),
        legend.position = c(.7, .15),
        legend.title = element_blank())
ggsave("../figs/design_effect_by_country_demo_weights.pdf", width = 6, height = 4.5)
ggsave("../figs/design_effect_by_country_demo_weights.png", width = 6, height = 4.5, dpi = 400)
```

### Comparing design effects with Internet population weights

Compute same quantities using the Internet-using adult population weights:
```{r}
w_v_uw_long_internet = waves_long %>%
  filter(!is.na(weight_internet_demo)) %>%
  as_survey_design(weights = weight_internet_demo) %>%
  group_by(country, country_code, name) %>%
  summarise(
    n = unweighted(n()),
    unweighted = unweighted(mean(value, na.rm = TRUE)),
    weighted = survey_mean(value, na.rm = TRUE, vartype = "ci", deff = TRUE)
  ) %>%
  group_by(country) %>%
  mutate(
    female_unweighted = unweighted[name == "female"]
  )
```

```{r}
adults_v_internet_long = bind_rows(
  w_v_uw_long %>% mutate(target_population = "adults"),
  w_v_uw_long_internet  %>% mutate(target_population = "Internet using adults")
) %>%
  group_by(country, name) %>%
  mutate(
    has_internet_weights = sum(n[target_population == "Internet using adults"]) > 100
  ) %>%
  filter(has_internet_weights, !is.na(country_code))
```

```{r}
adults_v_internet_long %>% 
  filter(name %in% c("know_positive_case")) %>%
ggplot(
  aes(x = reorder(substr(country, 1, 27), weighted_deff, max),
      y = weighted_deff, color = name, shape = target_population, group = target_population)
) +
  #facet_wrap(~ name, scales = "free_x") +
  coord_flip() +
  geom_line() +
  geom_point(fill = "white") +
  scale_color_brewer(palette = "Dark2") +
  scale_shape_manual(values = c(19, 21)) +
  scale_y_sqrt(breaks = seq(1, 5, by = .5), lim = c(1, 5)) +
  ylab("Design effect") +
  xlab("Country (sorted by design effect)") +
  guides(color = FALSE) +
  theme(#panel.grid.minor = element_blank(),
        legend.position = c(.7, .15),
        legend.title = element_blank())
ggsave("../figs/design_effect_by_country_demo_v_internet_weights.pdf", width = 4, height = 3)
ggsave("../figs/design_effect_by_country_demo_v_internet_weights.png", width = 4, height = 3, dpi = 400)
```


## Comparing results using demo and full survey weights
The two sets of weights allow for an internal falsification test, as they should produce results are consistent with each other.

Compute the same quantities as above with the full survey completion weights.
```{r}
w_v_uw_long_full = waves_long %>%
  filter(!is.na(weight_full_survey)) %>%
  as_survey_design(weights = weight_full_survey) %>%
  group_by(country, country_code, name) %>%
  summarise(
    n = unweighted(n()),
    unweighted = unweighted(mean(value, na.rm = TRUE)),
    weighted = survey_mean(value, na.rm = TRUE, vartype = "ci")
  ) %>%
  group_by(country) %>%
  mutate(
    female_unweighted = unweighted[name == "female"]
  )
```

```{r}
demo_v_full_long = bind_rows(
  w_v_uw_long %>% mutate(completion_type = "demo"),
  w_v_uw_long_full  %>% mutate(completion_type = "full")
) %>%
  group_by(country, name) %>%
  mutate(
    n_full = n
  ) %>%
  filter(!is.na(country_code))
```


```{r}
demo_v_full_long %>% 
  filter(name %in% c("female", "know_positive_case", "vaccine_accept")) %>%
ggplot(
  aes(x = reorder(substr(country, 1, 27), female_unweighted),
      y = weighted, ymax = weighted_upp, ymin = weighted_low,
      color = completion_type, shape = completion_type
      )
) +
  facet_wrap(~ name, scales = "free_x", nrow = 1) +
  coord_flip() +
  geom_pointrange(size = .3, position = position_dodge(width = .5)) +
  ylab("Weighted mean and 95% CI") +
  xlab("Country (sorted by unweighted % female)") +
  scale_color_manual(values = c("black", "blue")) +
  #scale_y_continuous(breaks = 1:5/10) +
  theme(panel.grid.minor = element_blank(),
        legend.position = "bottom")
ggsave("../figs/calibration_demographics_by_country_demo_v_full_weights.pdf", width = 7, height = 5.5)
ggsave("../figs/calibration_demographics_by_country_demo_v_full_weights.png", width = 7, height = 5.5, dpi = 400)
```
